Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-14 GHI_enh_Aeronet.tex
Commit 2024-05-02 09:10
Commit 2024-05-09 18:14
Commit 2024-05-14 11:35

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-01}

@@

\begin{verbatim}
[1] 2005.667
\end{verbatim}

@@

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Intercept
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Slope
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Month
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Zeropoint
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
SlopeRela
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
-810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
-6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
-1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
-982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
-140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
-3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
-1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
-2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
-1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
-1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
-1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
-1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
-1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
-1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
-262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
-745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
-122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
-474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
-1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
-2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
-1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
-1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
-1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
-1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
-1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
-1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
-243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
-708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
-109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
-441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
-1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
-2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
-1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
\end{longtable}

@@

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-14}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-16} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-40} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-41} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-42} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-43} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-44} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-45} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-46} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-47} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-48} \end{center}

SZA 55 : 0.00137369825595582

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Intercept
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Slope
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Month
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Zeropoint
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
SlopeRela
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
-810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
-6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
-1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
-982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
-140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
-3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
-1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
-2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
-1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
-1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
-1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
-1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
-1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
-1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
-262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
-745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
-122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
-474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
-1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
-2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
-1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
-1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
-1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
-1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
-1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
-1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
-243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
-708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
-109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
-441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
-1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
-2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
-1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
-847.8 & 0.7326 & 1 & 621.4 & SZA 55 & 2014 & 0.001179 \\
-787.2 & 0.6968 & 2 & 608.5 & SZA 55 & 2015 & 0.001145 \\
-1620 & 1.102 & 3 & 596.7 & SZA 55 & 2015 & 0.001848 \\
-1575 & 1.071 & 4 & 570.5 & SZA 55 & 2015 & 0.001877 \\
-1615 & 1.079 & 5 & 549.6 & SZA 55 & 2015 & 0.001964 \\
-288.8 & 0.4157 & 6 & 536.3 & SZA 55 & 2015 & 0.000775 \\
-483.7 & 0.5087 & 7 & 531.2 & SZA 55 & 2015 & 0.0009577 \\
-140.4 & 0.3406 & 8 & 549.3 & SZA 55 & 2015 & 0.0006201 \\
-415.5 & 0.4853 & 9 & 544.7 & SZA 55 & 2015 & 0.000891 \\
-1327 & 0.9475 & 10 & 576 & SZA 55 & 2015 & 0.001645 \\
-2204 & 1.393 & 11 & 567.8 & SZA 55 & 2015 & 0.002453 \\
-785.3 & 0.6983 & 12 & 618.3 & SZA 55 & 2014 & 0.001129 \\
\end{longtable}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-49} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-50} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-51} \end{center}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
year
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
typer
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
1997 & BR SZA 55 & 578.9 \\
2005 & SZA 55 & 576.4 \\
2005 & BR SZA 55 & 588.6 \\
2006 & SZA 55 & 574.9 \\
2007 & SZA 55 & 584.7 \\
2008 & SZA 55 & 615 \\
2011 & SZA 55 & 562.4 \\
2012 & SZA 55 & 582.9 \\
2013 & SZA 55 & 582.1 \\
2014 & SZA 55 & 594.3 \\
2015 & SZA 55 & 586.7 \\
2016 & SZA 55 & 583.9 \\
2017 & SZA 55 & 581.3 \\
2018 & SZA 55 & 581.2 \\
2019 & SZA 55 & 584.4 \\
2020 & SZA 55 & 600.3 \\
2021 & SZA 55 & 587.5 \\
2022 & SZA 55 & 587.4 \\
2023 & SZA 55 & 583 \\
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-52} \end{center}

### 2024-05-14 GHI_enh_CSid.tex
Commit 2024-05-14 11:35

\title{Enhancement of SDR in Thessaloniki Clear Sky}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-13}

@@

\begin{verbatim}
SZA median : 0.00184853525463023

@@

@@

@@

\DocumentationTok{\#\# for trend mean}
\CommentTok{\# trend\_apply  \textless{}{-} trend\_mean}
\CommentTok{\# trend\_factor \textless{}{-} {-}0.01995656}
\DocumentationTok{\#\# for trend median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}
\NormalTok{trend\_apply\_adj }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(tsy) \{}
  \FunctionTok{trend\_median}\NormalTok{(tsy) }\SpecialCharTok{{-}} \FloatTok{0.01995656}
\NormalTok{\}}

@@

\begin{verbatim}
[1] -0.01599489 -0.01332907
\end{verbatim}

@@

\begin{verbatim}
$mae
[1] 85.55033

$mse
[1] 8567.15

$rmse
[1] 92.5589

$mape
[1] 0.1365803

$nmse
[1] 0.1436112

$rstd
[1] 0.1400624
\end{verbatim}

@@

$objective
[1] 7042.576
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki Clear Sky}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-14}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-53} \end{center}

\begin{verbatim}
SZA median : 0.00184853525463023 
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-54} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-55} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-56} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-57} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-58} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-59} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-60} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-61} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-62} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-63} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-64} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-65} \end{center}

\begin{verbatim}
SZA 55 : 0.00137369825595582

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-66} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-67} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-68} \end{center}

@@

\DocumentationTok{\#\# for trend mean}
\CommentTok{\# trend\_apply  \textless{}{-} trend\_mean}
\CommentTok{\# trend\_factor \textless{}{-} {-}0.01995656}
\DocumentationTok{\#\# for trend median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_55}
\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}
\NormalTok{trend\_apply\_adj }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(tsy) \{}
  \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{{-}} \FloatTok{0.01995656}
\NormalTok{\}}

@@

\begin{verbatim}
[1] -0.01247017 -0.01039180
\end{verbatim}

@@

\begin{verbatim}
$mae
[1] 84.30937

$mse
[1] 8229.159

$rmse
[1] 90.71471

$mape
[1] 0.1351012

$nmse
[1] 0.1386586

$rstd
[1] 0.1375293
\end{verbatim}

@@

$objective
[1] 6810.44
\end{verbatim}

### 2024-05-14 article/article.tex
Commit 2024-05-14 11:35

Our dataset, after the data selection processing, consists of 6144534
records of GHI, of which \(1.906\,\%\) are CE and \(0.036\,\%\) are ECE
events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
The absolute stronger CE event had an OIR of \(353.46\,W/m^2\) on
21~June 2001. The relative stronger CE event was \(49.9\,\%\) above the
clear sky threshold, on 28~October 2016.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
autoregressive model with lag of 1 day, using the `maximum likelihood'
fitting method \citep{Gardner1980, Jones1980} by implementing the
function `arima' from the library `stats' of the R programming language
\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
error. We observe an increase of \(0.066\pm 0.08\,W/m^2/y\) on the mean
OIR.

@@

Although, the previous result is closer to the raw data, we preferred to
present the annual statistics, that give a more clear picture about the
long term CE trends. Hence, we calculated the annual values from the
one-minute measurements. The trend of OIR is \(0.03\pm 0.11\,W/m^2/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
not very useful due the intrinsic high variability of this metric.

@@

A better indicator of changes on the characteristic of CE would be the
number of CE occurrences and the total energy of the CE over irradiance.
The annual number of CE occurrences, shows a steady increase of
\(20.1\pm 22.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance on the atmosphere. The net sun radiation of the
region is not increased, but rather redistributed through the CE.
Although, the instantaneous values, can exceed the equivalent clear sky
irradiance to a considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
\(50.7\pm 71.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences.

@@

In order to further study the characteristics of the CE events, we
grouped the single minute CE events, to continuous CE groups (CEG).
Thus, a CEG consists of one or more successive CE cases, and can have a
duration of multiple of minutes. We have identified 30221 groups, where
the group with the longest duration lasted 140 minutes on 07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude that longer durations are getting increasingly rare, with
durations above 10 minutes very rare.

>>>>

Our dataset, after the data selection processing, consists of 6144534
records of GHI, of which \(1.95\,\%\) are CE and \(0.036\,\%\) are ECE
events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
The absolute stronger CE event had an OIR of \(353.05\,W/m^2\) on 24~May
2007. The relative stronger CE event was \(50.7\,\%\) above the clear
sky threshold, on 28~October 2016.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
autoregressive model with lag of 1 day, using the `maximum likelihood'
fitting method \citep{Gardner1980, Jones1980} by implementing the
function `arima' from the library `stats' of the R programming language
\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
error. We observe an increase of \(0.107\pm 0.08\,W/m^2/y\) on the mean
OIR.

@@

Although, the previous result is closer to the raw data, we preferred to
present the annual statistics, that give a more clear picture about the
long term CE trends. Hence, we calculated the annual values from the
one-minute measurements. The trend of OIR is \(0.08\pm 0.11\,W/m^2/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
not very useful due the intrinsic high variability of this metric.

@@

A better indicator of changes on the characteristic of CE would be the
number of CE occurrences and the total energy of the CE over irradiance.
The annual number of CE occurrences, shows a steady increase of
\(48.1\pm 23.8\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance on the atmosphere. The net sun radiation of the
region is not increased, but rather redistributed through the CE.
Although, the instantaneous values, can exceed the equivalent clear sky
irradiance to a considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
\(129.7\pm 74.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences.

@@

In order to further study the characteristics of the CE events, we
grouped the single minute CE events, to continuous CE groups (CEG).
Thus, a CEG consists of one or more successive CE cases, and can have a
duration of multiple of minutes. We have identified 30749 groups, where
the group with the longest duration lasted 140 minutes on 07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude that longer durations are getting increasingly rare, with
durations above 10 minutes very rare.
